MCC Models

### 2019-03-11 papers/full_paper/models.Rmd
update model param priors

---
title: "MCC Models"
author: "Manuel Bohn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

```{r model parameter adults}

# The prior on the speaker optimality parameter is largely positive but also contains negative values so that it could, in theory, result in a parameter that leads to model predictions below chance. The same prior is used for the intercept on children's parameters, where performance was below chance.  
speakOptParam <- '
var data = dataFromR.data

@@

  var speakerOptimality = uniformDrift({a: -3, b: 7, width: 0.2})

@@

```{r model setup ex 3 adults, include = FALSE}
# create datafiles with model parameters
model_params_ex3 <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  speak_opt = adult_model_param$so_map)

@@

```{r model rsa noise ex3 adults, include = FALSE}
predictions.rsa.ex3 <-'

@@

```{r predictions pragmatic model ex 3 adults, include = FALSE}
ex3_pragm_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3 , sep='\n'),
  data =list(data = model_params_ex3),
  data_var = "dataFromR"
)

@@

```{r model prior only ex3 adults, include = FALSE}
predictions.prior.only.ex3 <-'

@@

```{r predictions prior only model ex3 adults, include = FALSE}
ex3_prior_only_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3 , sep='\n'),
  data =list(data = model_params_ex3),
  data_var = "dataFromR"
)

@@

```{r model flat prior ex3 adults, include = FALSE}
predictions.flat.prior.ex3 <-'
var allData = dataFromR.data

@@

```{r predictions prior only model ex3 adults, include = FALSE}
ex3_flat_prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3 , sep='\n'),
  data =list(data = model_params_ex3),
  data_var = "dataFromR"
)

@@

```{r model setup ex 4, include = FALSE}

@@

```{r model rsa noise ex4 adults, include = FALSE}
predictions.rsa.ex4 <-'

@@

```{r predictions pragmatic model ex 4 adults, include = FALSE}
ex4_pragm_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4 , sep='\n'),
  data =list(data = model_params_ex4),
  data_var = "dataFromR"
)

@@

```{r model prior only ex4 adults, include = FALSE}
predictions.prior.only.ex4 <-'

@@

```{r predictions prior only model ex4 adults, include = FALSE}
ex4_prior_only_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4 , sep='\n'),
  data =list(data = model_params_ex4),
  data_var = "dataFromR"
)

@@

```{r model flat prior ex4 adults, include = FALSE}
predictions.flat.prior.ex4 <-'
var allData = dataFromR.data

@@

```{r predictions prior only model ex4 adults, include = FALSE}
ex4_flat_prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4 , sep='\n'),
  data =list(data = model_params_ex4),
  data_var = "dataFromR"
)

@@

```{r model parameters children}
# In theory, we would expect the speaker optimality parameter to always be positive. The prior for the intercept should therefore not include neagtive values. However, in the context of our study, the youngest children performed below chance and increased with age. This pattern can only be captured by the model if we allow the intercept to take negative values. To combine these considerations, the prior for the intercept is skewed towards being positive, but also includes negative values. The prior on the slope is agnostic about the shape of the developmental trajectory.
childModelParam <- '
var prefData = dataFromR.prefData
var infData = dataFromR.infData

@@

  var so_slope = uniformDrift({a: -5, b: 5, width: 0.2})
  var so_int = uniformDrift({a: -3, b: 7, width: 0.2})

@@

```{r inferring model parameters children}
# child_model_param<- webppl(
#   program_code = paste(rsaUtils, rsaModel, childModelParam , sep='\n'),
#   data = list(prefData = child_ex2_data, infData = child_ex1_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 7000, burn = 1000, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_model_param.rds")

>>>>

---
title: "MCC Models"
author: "Manuel Bohn"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

@@

```{r model parameter adults}
# Cauchy prior on the speaker optimality parameter around 1, based on previous work (e.g. Frank & Goodman, 2014) 
speakOptParam <- '
var data = dataFromR.data

@@

  var speakerOptimality = sample(Cauchy({location: 1, scale: 2}))

@@

```{r model setup ex 3 adults}
# create datafiles with model parameters
model_params_ex3 <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  speak_opt = adult_model_param$so_map)

@@

```{r model rsa noise ex3 adults}
predictions.rsa.ex3 <-'

@@

```{r predictions pragmatic model ex 3 adults}
ex3_pragm_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3 , sep='\n'),
  data =list(data = model_params_ex3),
  data_var = "dataFromR"
)

@@

```{r model prior only ex3 adults}
predictions.prior.only.ex3 <-'

@@

```{r predictions prior only model ex3 adults}
ex3_prior_only_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3 , sep='\n'),
  data =list(data = model_params_ex3),
  data_var = "dataFromR"
)

@@

```{r model flat prior ex3 adults}
predictions.flat.prior.ex3 <-'
var allData = dataFromR.data

@@

```{r predictions flat prior model ex3 adults}
ex3_flat_prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3 , sep='\n'),
  data =list(data = model_params_ex3),
  data_var = "dataFromR"
)

@@

```{r model setup ex 4}

@@

```{r model rsa noise ex4 adults}
predictions.rsa.ex4 <-'

@@

```{r predictions pragmatic model ex 4 adults}
ex4_pragm_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4 , sep='\n'),
  data =list(data = model_params_ex4),
  data_var = "dataFromR"
)

@@

```{r model prior only ex4 adults}
predictions.prior.only.ex4 <-'

@@

```{r predictions prior only model ex4 adults}
ex4_prior_only_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4 , sep='\n'),
  data =list(data = model_params_ex4),
  data_var = "dataFromR"
)

@@

```{r model flat prior ex4 adults}
predictions.flat.prior.ex4 <-'
var allData = dataFromR.data

@@

```{r predictions flat prior model ex4 adults}
ex4_flat_prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4 , sep='\n'),
  data =list(data = model_params_ex4),
  data_var = "dataFromR"
)

@@

```{r model parameters children}
# The prior on the speaker optimality intercept is the same as for the adult speaker optimality parameter.

childModelParam <- '
var prefData = dataFromR.prefData
var infData = dataFromR.infData

@@

  var so_slope = sample(Cauchy({location: 0, scale: 2}))
  var so_int = sample(Cauchy({location: 1, scale: 2}))

@@

```{r inferring model parameters children}
# child_model_param<- webppl(
#   program_code = paste(rsaUtils, rsaModel, childModelParam , sep='\n'),
#   data = list(prefData = child_ex2_data, infData = child_ex1_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_model_param.rds")
